Calculating Entropies With Nested Sampling

### 2017-02-04 paper/ms.tex
Mention common random number technique

>>>>

The mutual information is equal to $H_{\x} + H_{\d} - H_{\x, \d}$. The
uncertainties in each of these three quantities is quite large, and would lead
to a large uncertainty on $I_{\x, \d}$ if computed naively. To reduce this
uncertainty, we computed the three entropies using a common random number
generator for the reference pairs. This is an example of the
{\em common random numbers} technique of variance reduction.
